Boycotts require significant deterioration in a company's public image to have an impact on their stock prices.

### 2024-04-26 paper/paper.qmd
cleaning up the files

## Detailed Observation of Change in Stock Price
In @tbl-twoweeksNKEprotest, the daily difference in Nike's stock price following the international Global Exchange protest. The largest change is a week after the protest on the 27th with a drop in 5.79% or 35 cents. For a better understanding of the overall decline in 1997, @fig-linegraphNKEfocused shows changes in Nike's stock price. The company sees growth early in the year until a rapid drop from mid-February to mid-April. Another significant drop is from August until the end of the year.

>>>>

## Detailed Observation of Change in Stock Price
In @tbl-twoweeksNKE, the daily difference in Nike's stock price following the international Global Exchange protest. The largest change is a week after the protest on the 27th with a drop in 5.79% or 35 cents. For a better understanding of the overall decline in 1997, @fig-linegraphNKEfocused shows changes in Nike's stock price. The company sees growth early in the year until a rapid drop from mid-February to mid-April. Another significant drop is from August until the end of the year.
